Colonies - Compute Continuums across Platforms

### 2023-04-13 paper_2023/paper.tex
second draft3

\section{Use cases}
Colonies is currently used commerically by a startup company called RockSigma AB\footnote{https://www.rocksigma.com} to implement a compute engine for analysing seismic activities in underground mines. This section will not dig into the details of this specific implementation; instead it will provide an outline of potential future use cases in which Colonies could make a considerable impact.

>>>>

\section{Use cases}
Colonies is currently used commerically by a startup company called RockSigma AB\footnote{https://www.rocksigma.com} to implement a compute engine for analysing seismic activities in underground mines. The paper will not explain the details of this specific implementation; instead it will outline other potential use cases where Colonies could make a considerable impact.
